Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
new intro
describe Redis

The caching proxy consists of several components, detailing the
overview in Figure~\ref{fig:arch}:

@@

Analysers and prefetchers run asynchronously with query
evaluation. This is achieved by an addition to the proxy that sends a
query to a persistent analyser script that subscribes to a channel on
a Redis\footnote{See \url{http://redis.io/}} data structure store.

>>>>

It is interesting to add further implementation details to the
overview in Figure~\ref{fig:arch} with a list of the implemented
components of the caching proxy:

@@

Analysers and prefetchers run asynchronously with query
evaluation. This is achieved by an addition to the proxy that sends a
query to a persistent analyser script that subscribes to a channel on
a Redis\footnote{See \url{http://redis.io/}} data structure store. The
Redis data structure store is a mostly-memory ``NoSQL'' database for
storing primitive data structures identified by a key.
